---
title: "RC 159-5: Evaluation of three differents to coltrol red slime"
author: ron Collins
Date: 
output:
  pdf_document: default
  word_document: default
  html_notebook: default
  html_document: default
---
# Introduction
  Tissue culture tube with callus in Bldg. 001, Rm. 331 after six months are beginning to be contaminated with a red slime.  Consequently, it became imperitive that we find a way to control the bacteria.  Evidently PPm wasn't working.  Maybe at a higher concenation. A series of experiments were planned to evaluate different antibiotics that we have used in the past ro control the bacteria.


```{r load packages, echo = FALSE, warning=FALSE, message=FALSE}
# load required packages
library(readxl)
library(car)
library(data.table)
library(dplyr)
library(tidyr)
```

```{r input RC159_5, echo = FALSE}
#data inout
RC159_5Data <- read_excel("RC159_5.xlsx", sheet = 1, col_names = TRUE, col_types = NULL, na = "NA", skip = 0)
```


```{r  convert, echo = FALSE}
# Convert variable type to factor
RC159_5Data$Trt <- as.factor(RC159_5Data$Trt)
RC159_5Data$concBac <- as.factor(RC159_5Data$concBac)

```

### summary
  The following is a summary of the treatments ( antibiotics and no antibiotics) by bacterial concentration. 
```{r summary, echo = FALSE, message=FALSE}
### group mtcars by cylinders and return some averages
RC159_5DataSum <- RC159_5Data %>%
select(Trt, concBac, count) %>%
group_by(Trt,concBac) %>%
summarise(Total_mean = mean(count))
RC159_5DataSum
```



### analysi of variance for total area
```{r echo = FALSE}
# Analysis for Differ
 prelim.lm <- lm(formula = count ~ Trt +  concBac + Trt*concBac, data = RC159_5Data, na.action=na.omit)
summary(prelim.lm)

Anova(prelim.lm,type='II')
```
### pair wise t test diff vs PlantId
```{r echo = FALSE}
pairwise.t.test(RC159_5Data$count, RC159_5Data$Trt)
```



```{r control removed, echo=FALSE, message=FALSE}
# Control removed from dataframe

RC159_5Data <- RC159_5Data %>%
    filter(concBac != 0)
```

### summary
```{r echo = FALSE}
RC159_5DataSum <- RC159_5Data %>%
select(Trt, concBac, count) %>%
group_by(Trt,concBac) %>%
summarise(Total_mean = mean(count))
RC159_5DataSum
```


### analysi of variance for colony count
```{r echo = FALSE}
# Analysis for Differ
 prelim.lm <- lm(formula = count ~ Trt +  concBac + Trt*concBac, data = RC159_5Data, na.action=na.omit)
summary(prelim.lm)

Anova(prelim.lm,type='II')
```
### pair wise t test count  vs Trt
```{r echo = FALSE}
pairwise.t.test(RC159_5Data$count, RC159_5Data$Trt)
```


### pair wise t test count  vs concBac
```{r echo = FALSE}
pairwise.t.test(RC159_5Data$count, RC159_5Data$concBac)
```