---
output:
  html_document: default
  word_document: default
---
----
title: "RC RC 159-5 Analysis of control of rec bacterial contamination by 3 antibiotics"
author: "Ron Collins"
date: "`r Sys.Date()`"
output: 
  word_document: default
  html_notebook: default
  html_document: default
  pdf_document: default
---
# Introduction
  Tissue culture tube with callus in Bldg. 001, Rm. 331 after six months are beginning to be contaminated with a red slime.  Consequently, it became imperitive that we find a way to control the bacteria.  Evidently PPm wasn't working.  Maybe at a higher concenation. A series of experiments were planned to evaluate different antibiotics that we have used in the past ro control the bacteria.  The first group of Antibiotic's used are Tetracycline HCl, mg Streptomycin Sulfate, and Chloramphenicol. They will be used at the same rates from prior experiments: 25 mg/liter.
  This is for the first experimental replicate.



```{r load packages, echo = FALSE, warning=FALSE, message=FALSE}
# load required packages
library(readxl)
library(car)
library(data.table)
library(dplyr)
library(tidyr)
```

```{r input RC159_5, echo = FALSE}
#data inout
RC159_5Data <- read_excel("RC159_5.xlsx", sheet = 1, col_names = TRUE, col_types = NULL, na = "NA", skip = 0)
```


```{r  convert, echo = FALSE}
# Convert variable type to factor
RC159_5Data$Trt <- as.factor(RC159_5Data$Trt)
RC159_5Data$concBac <- as.factor(RC159_5Data$concBac)

```

### summary with background control included
  The following is a summary of the treatments ( antibiotics and no antibiotics) by bacterial concentration. 
```{r summary, echo = FALSE, message=FALSE}
### group mtcars by cylinders and return some averages
RC159_5DataSum <- RC159_5Data %>%
select(Trt, concBac, count) %>%
group_by(Trt,concBac) %>%
summarise(Total_mean = mean(count))
RC159_5DataSum
```
From looking at the counts, it appears that the only difference is between bacteria concentration.


### analysis of variance for bacterial count as a result of antibiotics with background control.
```{r echo = FALSE}
# Analysis for Differ
 prelim.lm <- lm(formula = count ~ Trt +  concBac + Trt*concBac, data = RC159_5Data, na.action=na.omit)
summary(prelim.lm)

Anova(prelim.lm,type='II')
```
### pair wise t test Count vs trt with background control included
```{r echo = FALSE}
pairwise.t.test(RC159_5Data$count, RC159_5Data$Trt)
```
  The results are skewed because of the background control.  I do not put much faith in the results.
  
  
### pair wise t test count  vs concBac with background control included
```{r echo = FALSE}
pairwise.t.test(RC159_5Data$count, RC159_5Data$concBac)
```
  The results are skewed because of the background control.  I do not put much faith in the results. 

```{r control removed, echo=FALSE, message=FALSE}
# Control removed from dataframe

RC159_5Data <- RC159_5Data %>%
    filter(concBac != 0)
```

### summary with background control removed
```{r echo = FALSE}
RC159_5DataSum <- RC159_5Data %>%
select(Trt, concBac, count) %>%
group_by(Trt,concBac) %>%
summarise(Total_mean = mean(count))
RC159_5DataSum
```


### analysi of variance for colony count with background control removed
```{r echo = FALSE}
# Analysis for Differ
 prelim.lm <- lm(formula = count ~ Trt +  concBac + Trt*concBac, data = RC159_5Data, na.action=na.omit)
summary(prelim.lm)

Anova(prelim.lm,type='II')
```
### pair wise t test count  vs Trt with background control removed.
```{r echo = FALSE}
pairwise.t.test(RC159_5Data$count, RC159_5Data$Trt)
```


### pair wise t test count  vs concBac with background control removed
```{r echo = FALSE}
pairwise.t.test(RC159_5Data$count, RC159_5Data$concBac)
```