
---
title: "RC 159-5.4a: Evaluation of three different of PPM to coltrol red slime"
author: Ron Collins
Date: 
output:
  word_document: default
  pdf_document: default
  html_notebook: default
  html_document: default
---
# Introduction
       Tissue culture tubes containing callus in Bldg. 001, Rm. 331 after six months are beginning to be contaminated with a red slime.  Consequently, it became imperative that we find a way to control the bacteria.  Evidently PPm at 0.1 % wasn't working.  Initially the five antibiotics used in prior research were evaluated at the recommended rate and three times the recommended rate.None of the antibiotic treatments were significantly different from the control.  It was decided to test PPM at 1 and 10% for control of the red bacteria.


```{r "load packages", echo = FALSE, warning=FALSE, message=FALSE}
# load required packages
library(readxl)
library(car)
library(data.table)
library(dplyr)
library(tidyr)
```

```{r input RC159_5, echo = FALSE}
#data inout
RC159_5.4.0Data <- read_excel("RC159_5.4.0.xlsx", sheet = 1, col_names = TRUE, col_types = NULL, na = "NA", skip = 0)
```




```{r  convert, echo = FALSE}
# Convert variable type to factor
RC159_5.4.0Data$trt <- as.factor(RC159_5.4.0Data$trt)

```

### summary
  The following is a summary of the treatments (0, 1% & 10% PPM) for bacteria count 
```{r summary, echo = FALSE, message=FALSE}
### group mtcars by cylinders and return some averages
RC159_5.4.0DataSum <- RC159_5.4.0Data %>%
select(trt, Count) %>%
group_by(trt) %>%
summarise(Total_mean = mean(Count))
RC159_5.4.0DataSum
```



### analysi of variance for total area
```{r echo = FALSE}
# Analysis for Differ
 prelim.lm <- lm(formula = Count ~ trt, data = RC159_5.4.0Data, na.action=na.omit)
summary(prelim.lm)

Anova(prelim.lm,type='II')
```
### pair wise t test Trt vs Count
```{r echo = FALSE}

pairwise.t.test(RC159_5.4.0Data$Count, RC159_5.4.0Data$trt)
```

### Results
    The ANOVA for three treatments were significantly differet . In the Pairwise comparison of the three treatments, The 0% treatmment differed from 1 & 10 %. The 1 and 10% were not signifficantly different
    Form Prior studies none of the five antiobiotics that we have used in prior research had any effect on the red bacteria at the recommened rate or at 3 times recommended rate.
The PPM at 1 & 3% gave 100% control. The question
